\documentclass[a4paper,12pt]{report}
\usepackage{fullpage}
\usepackage{sectsty}
\usepackage{mdwlist}
\usepackage{setspace}
\onehalfspacing

\sectionfont{\large}
\subsectionfont{\normalsize}

\begin{document}

\begin{Large}
\begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}} p{0.65\textwidth} p{0.5\textwidth} }
Benjamin J Kero & ben.kero@gmail.com \\
Portland, OR & (425) 591-2443 \\
\end{tabular*}
\end{Large}

\section*{Summary of Expertise}
\begin{itemize}
\item Administration of Linux distributions including RHEL/CentOS, Ubuntu, Debian, and Gentoo.
\item Collaboration with external groups including open source project leaders/members, vendors, volunteers, and communities.
\item Installing, administrating, debugging, and populating Nagios, Cacti, Munin, Ganglia, Apache HTTPD, Varnish, MySQL, cfEngine, Puppet, Bugzilla, RT, Subversion, Git, Mercurial.
\item Working knowledge of DNS, NFS, FTP, SSH, IRC, and other common services.
\item Use of Python, PHP, C/C++, perl, awk, sed, and BASH scripting to debug applications and in the creation and improvement of internal tools.
% \item Familiarity with ARM, MIPS, x86, x86\_64, PowerPC, PPC64, IBM Cell, and SPARC architectures.
\end{itemize}

\section*{Experience}

\subsection*{Senior System Administrator, Mozilla, 06/2010 -- Present}
\begin{itemize}
\item Responsible for availability, consistency, development, and scaling of source code repository infrastructure.  Coordinated with Mercurial project to design goals for new versions, corrected code bugs, and tuned infrastructure for high-traffic serving.
\item Designed, implemented, and deployed scalable monitoring and trending infrastructure using Ganglia to monitor thousands of machines at multiple datacenters worldwide.
\item Deployed clustering virtualization using Ganeti virtualization management software. Automated machine deployment with PXELinux, Kickstart, and Puppet.
\item Participated in 24-hour on-call rotation. Responsible for critical infrastructure availability including application debugging, multi-host service clusters, and priority escalation.
\end{itemize}

\subsection*{Systems Operations, Google, 09/2008 -- 12/2008}
\begin{itemize}
\item Contributed code, documentation, and unit tests to in-house log aggregation software as part of a development team. Designed to be fast, massively scalable, and fault tolerant to hardware failure and network outage.
\item Added log aggregation software installation and automated configuration to internal deployment system for office-in-a-box installations.
\item Participated in code reviews for all team-submitted code.
\end{itemize}

\subsection*{System Administrator Intern, Intel, 06/2008 -- 09/2008}
\begin{itemize}
\item Wrote and implemented rack and inventory management system using PHP, MySQL, and MsSQL.
\item Assisted in designing, implementing, and upgrading proprietary in-house configuration management system to a standardized cfEngine system.
\item Triaged, escalated, and handled change orders, bugs, and bad states using BMC Remedy software.
\end{itemize}

\subsection*{Systems Administrator, OSU Open Source Lab, 09/2006 -- 12/2010}
\begin{itemize}
\item Populated cfEngine management configurations for role-based instantiation of servers in addition to updating and repairing damaged or externally modified configurations. Assisted in cfEngine to Puppet host transition.
\item Configured, troubleshooted, and repaired various open-source services, such as Apache, PHP, MySQL, Nagios, Cacti, Munin, RT, and Subversion.
\item Collaborated with open source communities for service availability and remote work.
\end{itemize}

\section*{Speaking Engagements}
\begin{itemize}
        \item \textbf{How to use Puppet like an Adult}, FOSS.in, Bangalore, India. Linux.Conf.Au, Canberra, Australia. 2012-2013.
        \item \textbf{The Art of Open Source DJing}, Open Source Bridge, Portland, Oregon. 2012.
        \item \textbf{Ganeti: Clustered Virtualization on Commodity Hardware}, Portland ACM, Portland, Oregon. Linux.Conf.Au, Ballarat, Australia. 2012.
        \item \textbf{IT@Mozilla: Open Sourcing the Infrastructure}, Free and Open Source Software Developers\' European Meeting, Brussels, Belgium. 2012.
        \item \textbf{IT and Community} Mozcamp Asia, Singapore. 2011.
        \item \textbf{The Dark Arts of SSH}, Beaver Bar Camp, Corvallis, Oregon. 2011.
\end{itemize}

\section*{Education}

\subsection*{Computer Science, Oregon State University, 09/2006 -- 12/2010}
\begin{itemize}
\item Attained Bachelor’s degree in Computer Science with a focus of Information Technology, and minor in Business Administration.
\item Wrote Linux kernel modules and schedulers including a customisable disk scheduler, process scheduler, USB device driver, and memory allocator.
\item Designed a content management system in a LAMP environment using PHP, HTML, JavaScript, and CSS. Practiced federally usability and accessibility guidelines as well as standard coding techniques for handicapped viewers and screen-readers.
\item Participated in ongoing biotechnology projects by creating system for public submission, customizable analysis, and anonymous retrieval of whole-genome datasets.

\end{itemize}

\end{document}
